---
title: "Bayes-Snap"
author: "Cade Garcia"
date: "2024-11-12"
output: html_document
---

# Notes

-   Data comes from *United States Census Bureau*

-   ACS = American Community Survey

-   we could talk about race since the data is there, but honestly that's too fragile of a topic 

## Interest Tables

|  |  |  |  |  |
|--------------|------------|---------------|----------------|----------------|
| Table Code |  | **Households that receive snap** |  | Table Code |
| S2201_C03_004 | Married | Vs | Non-married | S2201_C03_005 |
| S2201_C03_007 | Female (no spouse) | Vs | Male (no spouse) | S2201_C03_006 |

|  |  |  |  |  |
|----------------|------------|-------------|----------------|----------------|
| Table Code |  | **Households that don’t receive snap** |  | Table Code |
| S2201_C05_004 | Married  | Vs | Non-married | S2201_C05_005 |
| S2201_C05_007 | Female (no spouse) | Vs | Male (no spouse) | S2201_C05_006 |

|  |  |  |  |  |
|---------------|-----------------|------|--------------------|---------------|
| Table Code | **Receives snap** |  | **Doesn’t receive snap** | Table Code |
| S2201_C03_034 | Median income (dollars)  | Vs | Median Income (dollars) | S2201_C05_034 |

# Code

## Libraries

```{r}
library(tidyverse)
library(tidycensus)
library(ggplot2)
```

## Loading variables

```{r}
acs5 <- load_variables(2022, "acs5", cache = TRUE)
View(acs5)
```

```{r}
acs1 <- load_variables(2023, "acs1", cache = TRUE)
View(acs1)
```

## Loading Data "S2201"

[*Food Stamps/Supplemental Nutrition Assistance Program (SNAP)*](https://data.census.gov/table/ACSST5Y2022.S2201?q=snap%20acs5%20in%20Hawaii)

```{r}
# Loads data into a data frame
snap_2023 <- get_acs(geography = "tract",
                     state = "HI", 
                     table = "S2201", 
                     survey = "acs5", 
                     year = 2022,
                     output = "wide",
                     cache = TRUE)
View(snap_2023)
```

## Plotting

find important variables to use when we create a new data set.

```{r}
ggplot(snap_2023, aes(S2201_C03_007E, S2201_C03_006E)) +
  geom_point() +
  labs(title = "Female vs Male households that recieve snap (no spouse)",
       x = "Female", 
       y = "Male")
```
